Fig1

### 2020-08-07 analysis/figure-1.Rmd
new suppl fig 1

```{r setup, include=T}
library(tidyverse)
library(cowplot)
library(Rtsne)

@@

```{r}
# pca relies on count data from limma
pca_h1 <- subsetmakepca("hypothalamus", alllevels, sexlevels)	
pca_h2 <- makefvizdf("hypothalamus", alllevels, sexlevels)

@@

```{r supplfig, fig.height=7.25, fig.width=7.25}

@@

pdf(file="../figures/supplfig-1.pdf", width=7.5, height=7.5)
plot(supplfig)
dev.off()

png("../figures/supplfig-1.png", width = 7.5, height = 7.5, 
    units = 'in', res = 300)
plot(supplfig)  
dev.off()

>>>>

```{r setup, include=T}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(factoextra)
library(ggsignif)

@@

```{r pca}
# pca relies on count data from limma
pca_h1 <- subsetmakepca("hypothalamus", alllevels, sexlevels)	
pca_h2 <- makefvizdf("hypothalamus", alllevels, sexlevels)

@@

```{r supplfig-1, fig.height=7.25, fig.width=7.25}

@@

pdf(file="../figures/supplfig-1-1.pdf", width=7.5, height=7.5)
plot(supplfig)
dev.off()

png("../figures/supplfig-1-1.png", width = 7.5, height = 7.5, 
    units = 'in', res = 300)
plot(supplfig)  
dev.off()
